---
title: "Basketball Plot Stars"
authors: "Nicholas Brimhall, J Cook, Grace Russell, and Matthew White"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vinyette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(projectr5555)
```

<https://github.com/Hoolahups/projectr5555>

## Overview

Basketball enthusiasts and analysts often seek robust and intuitive
tools to visualize player and team performance data quickly. This
package, projectr5555, offers a straightforward and flexible way to
scrape and plot NCAA basketball team statistics. Whether the user is
tracking player progress, comparing team statistics, or scouting
opponents, projectr5555 provides the tools users need to make informed
decisions and compelling presentations. Utilizing this package, users
can effortlessly compare players across multiple metrics through visual
representations, allowing for quick insights and deep analysis.

### Data

The get_data function takes a URL as an argument and scrapes the
corresponding webpage. Many NCAA basketball teams use a format for their
website identical to USU's, and so this function works for any team
using that format. The function checks that the HTML scraped from the
website matches an expected format, but the user should check to make
sure that the desired team statistics page looks visually similar to
USU's. The URL can be found by visiting the desired NCAA basketball
team's athletic page and navigating to the stats page.

```{r, include = TRUE}
usu_t2023 <- get_data("https://utahstateaggies.com/sports/mens-basketball/stats
                      /2023-24")
```

To obtain the URL for another team visit the desired NCAA basketball
team's athletic page and navigating to the stats page. Select the
desired season and copy the URL. The example below shows how the user
can get the data for the University of Connecticut, the 2024 NCAA
tournament champions, use the URL.

```{r, include = TRUE}
uconn_t2023 <- get_data("https://uconnhuskies.com/sports/mens-basketball/stats
                        /2023-24")
```


### Plots


#### Star Plot

This plot visualizes a specified player's statistics in a star chart, highlighting their performance across multiple areas like scoring, defense, and rebounding. There are eight default statistics. Each axis represents a different stat, providing a quick visual assessment of a player's skills. The function takes the team and players name as the first two arguments. 

```{r, include = TRUE}
player_star(usu_t2023, "osobor_great")

```


#### Bar Plot

This horizontal bar plot compares a single statistic, such as field goal percentage, across all team members. It quickly identifies top performers and those needing improvement in specific areas.

```{r, include = TRUE}
team_bar(usu_t2023, "FG_pct")
```


#### Scatter Plot

This scatter plot compares two statistics to explore their relationship, such as the correlation between overall shooting efficiency and three-point shooting. It helps identify patterns that can inform coaching strategies.

```{r, include = TRUE}
compare_stats(usu_t2023, "FG_pct", "X3PT_pct")
```


### Make Your Own Variables

The variable_maker function takes two existing variables and combines them
in a way that the user specifies. It then returns the entire list with the
variables and average added to it.

```{r, include = TRUE}
usu_t2023 <- variable_maker(usu_t2023, "GP", "GS", "sum", "gps")
```

Once you have your new variable, you can use it to make your own plots.
Whether or not its useful is up to you, but make sure to have fun with
it!

```{r, include = TRUE}
player_star(usu_t2023, "martinez_ian", vars = c("GP", "GS", "FGA", "X3PT", "gps"
))
```


## Summary

The plotting capabilities provided by projectr5555 are invaluable for
visualizing complex basketball statistics in a clear and accessible
manner. These plots not only enhance understanding and presentation of
player and team metrics but also aid in strategic decision-making.
Whether for fan engagement, coaching strategies, or academic research,
our tools offer significant benefits to diverse users.
