---
title: "Basketball Plot Stars"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vinyette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup, include = FALSE}
library(projectr5555)
```
https://github.com/Hoolahups/projectr5555

Our package scrapes player statistics for a university basketball team from the official team website and provides functions to create user-specified plots. 

The get_data function takes a URL as an argument and scrapes the corresponding webpage. Many NCAA basketball teams use a format for their website identical to USU's, and so this function works for any team using that format. The function checks that the HTML scraped from the website matches an expected format, but the user should check to make sure that the desired team statistics page looks visually similar to USU's.


```{r, include = TRUE}
usu_t2023 <- get_data("https://utahstateaggies.com/sports/mens-basketball/stats/2023-24")
```

The player_star function takes the team as an argument, and one of the players
from the team as an argument. The function creates a star plot of eight default
statistics about the player.

```{r, include = TRUE}
player_star(usu_t2023, "osobor_great")
```

The team_bar function creates a horizontal bar plot. It takes the team and 
a stat as arguments, and it compares who has the highest and lowest of these
statistics.

```{r, include = TRUE}
team_bar(usu_t2023, 'FG_pct')
```

The compare_stats function creates a scatterplot of two statistics from the
team. It takes a team argument, and two stats must be chosen to compare.

```{r, include = TRUE}
compare_stats(usu_t2023, 'FG_pct', 'X3PT_pct')
```
